Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators

### 2019-09-12 GWLDCII.tex
minor fixes

  \begin{align*}
    I_1^{W} & = I_1^{V} \cup \{n-3\} \\
    I_n^{W} & = I_1^{V} \cup \{n\} \\
    I_{n-1}^{W} & = I_n^{V} \cup \{n-1\} \\
    I_{n-2}^{W} & =
    \begin{cases}
      I_{n-2}^{V}\cup \{n-2\} & \text{if $n-2\not\in I_{n-2}^{V}$} \\
      I_{n-2}^{V}\cup \{n-1\} & \text{if $n-2\in I_{n-2}^{V}$, $n-1\not\in I_{n-2}^{V}$} \\
      (I_{n}^{V} - \{n-5\})\cup \{n-1,n-2\} & \text{if $n-1, n-2\in I_{n-2}^{V}$}
    \end{cases} \\
    I_{k}^{W} & =
    \begin{cases}
      I_k^{V}\cup \{n-3\} & \qquad \qquad \qquad \qquad \text{if $n-3 \not\in I_k^{V}$}\\
      I_k^{V}\cup\{n-2\} & \qquad \qquad \qquad \qquad \text{if $n-3\in I_k^{V}$}
    \end{cases} \\
    & \text{for $1<k<n-2$}
  \end{align*}
\end{lem}

@@

@@

We first consider $I_1^{W}$. Note that $n-3 \not\in I_1^{V}$: \hlfix{for Case 2 this is clear from the diagram (since Algorithm {\ref{alg:put GN on WLD}} would force $q$ to contribute no later than vertex $n-4$),}{why? isn't obvious to me without several cases, and even then}\note{yeah, I can't see this either; cyclic intervals is probably a better argument} while for Case 1 it follows directly from Lemma \ref{lem no fourth vertex}. Therefore when we start at vertex 1 and apply the Grassmann necklace algorithm to $W$, $p$ is the \st{only remaining unassigned propagator when we reach vertex $n-3$}{\color{violet}last propagator to contribute}, and so we have $ I_1^{W}(p) = n-3$ and $I_1^W = I_1^V\cup \{n-3\}$.

@@

\note{When doing the final formatting, try to ensure that Figure \ref{fig Le} and Lemma \ref{lem shape} are on the same page}
\begin{lem}\label{lem shape}
  Let $V$ and $W$ be as in Lemma~\ref{lem I}.
  The shape of the Le diagram of $V$ can be built from left to right of the following blocks: a rectangle which is 3 columns wide, one more column of the same height, and a partition shape with at most as many rows as the rectangle.
  The shape of the Le diagram of $W$ can be built from left to right of the following blocks: a rectangle with 3 columns and one more row than the first rectangle of $V$, and the same partition shape as in $V$.
\end{lem}

@@

Also by Lemma~\ref{lem I} we have $I_{n-1}^{W} = I_n^{V} \cup \{n-1\}$. Recall from the proof of Lemma \st{{\ref{lem I}}} {\color{violet} {\ref{lem shape}} }\sanote{change back if actually in 4.4} that $n-3,n-2,n-1,n \not\in I_1^V$; therefore $I_1^W\setminus I_{n-1}^W = (I_1^V \setminus I_n^V) \cup\{n-3\}$, and $n-3$ is maximal in this set. Similarly, 
\[I_{n-1}^W \setminus I_1^W = (I_n^V \setminus I_1^V) \cup \{n-1\} \subseteq \{n-1,n\},\]
where the final inclusion follows from the definition of Grassmann necklace\sanote{why only $\{n-1,n\}$? I'd believe an inclusion the other way}\note{Definition of GN: $I_1 = (I_n\setminus\{n\})\cup\{\text{something}\}$}. In particular, $n-1$ is minimal in this set, so Algorithm~\ref{alg:GN to Le} yields a plus in the $(n-3) \rightarrow (n-1)$ position (i.e. the second box in the bottom row of the Le diagram of $W$) \hlfix{along with any plusses yielded by $I_n^V$.}{display seems to imply that there is exactly one such other $+$. Is this correct?}\note{Display implies there's at most one, but if we apply no coloops I think that becomes exactly one.}
\end{proof}

@@

  First note that a Wilson loop diagram $W$ with one propagator supported on vertices $i<i+1<j<j+1$ has a Le diagram consisting of a single row with $n-i$ boxes. The columns are labeled from left to right by $n, \ldots, i+1$. By Algorithm~\ref{alg:GN to Le} there are plusses in the $i+1$, $j$, and $j_1$ positions. \sanote{changed for grammar and notational consistency. check}

  Now consider Wilson loop diagrams with $k>1$ propagators.  By Lemma~\ref{lem uncovered} it suffices to prove the result for weakly admissible Wilson loop diagrams with $k$ propagators and no non-supporting vertices.  By Lemma~\ref{lem dihedral} it suffices to prove the result for at least one Wilson loop diagram from each dihedral orbit. In particular, consider $W$, which after possible dihedral transformation, has a propagator $p$ with the properties in Lemma~\ref{lem good p}.

  We make one further simplification: if our $W$ is in Case 2 of Figure~\ref{fig special p} and $n-1$ supports only $p$ but $n-2$ supports at least one other propagator\sanote{?? see para below}, then flip $W$ on the line perpendicular to the $(n-2){th}$ edge to obtain a diagram with the configuration of Case 1. This eliminates the possibility that we could have $n-2 \in I_{n-2}^W$ but $n-1 \not\in I_{n-2}^W$.

{\color{violet} I'm very confused about the previous paragraph. I thought that by constuction, in case 2, there can be exactly 2 propagators ending on edge $n-3$, $p$ and $q$. I also thought the distinguising feature between the two subcases of Figure 10 case 2 in Lemma 4.4 $I_{n-2}^W$ was the presence or absense of a propagator $r$ ending on edge $n-1$. If $r$ exists, $n-1 \in I_{n-2}^V$ and if  $r$ doesn't exist, $n-1 \not \in I_{n-2}^V$.}

>>>>

@@

  \begin{align*}
    I_1^{W} & = I_1^{V} \cup \{n-3\} \\
    I_n^{W} & = I_1^{V} \cup \{n\} \\
    I_{n-1}^{W} & = I_n^{V} \cup \{n-1\} \\
    I_{n-2}^{W} & =
    \begin{cases}
      I_{n-2}^{V}\cup \{n-2\} & \text{if $n-2\not\in I_{n-2}^{V}$} \\
      I_{n-2}^{V}\cup \{n-1\} & \text{if $n-2\in I_{n-2}^{V}$, $n-1\not\in I_{n-2}^{V}$} \\
      (I_{n}^{V} \setminus \{n-5\})\cup \{n-1,n-2\} & \text{if $n-1, n-2\in I_{n-2}^{V}$}
    \end{cases} \\
    I_{k}^{W} & =
    \begin{cases}
      I_k^{V}\cup \{n-3\} & \qquad \qquad \qquad \qquad \text{if $n-3 \not\in I_k^{V}$}\\
      I_k^{V}\cup\{n-2\} & \qquad \qquad \qquad \qquad \text{if $n-3\in I_k^{V}$}
    \end{cases} \\
    & \text{for $1<k<n-2$}
  \end{align*}
\end{lem}

@@

\note{Following two paragraphs added to replace the sentence ``clearly $n-3 \not\in I_1^V$''}
We first show that $n-3 \not\in I_1^V$. In Case 1, the only way we could have $n-3 \in I_1^V$ is if $V$ admits some propagator $r$ with $I_1(r) = n-3$; from the figure, one end of $r$ would have to lie on edge $n-4$, and by Lemma~\ref{lem no fourth vertex} the other end would have to lie on edge $n-1$ or $n$. However, if $r = (n-4,n-1)$ then by [remark following cyclic intervals lemma] we would have $I_1^V(r) = n-4$, while if $r = (n-4,n)$ then $r$ is the clockwise-most propagator supported on vertex 1 and we would have $I_1^V(r) = 1$. Either way, we have $I_1^V(r) \neq n-3$.

In Case 2 the only propagator supported on vertex $n-3$ in $V$ is $q$, and by [cyclic intervals remark] we have $I_{n-1}^V(q) = n-5$. Further, it must also be the case that $I_n^V(q) = n - 5$: if $n-1$ is non-supporting in $V$ then this is immediate, while if there exists a propagator $r$ in $V$ with $I_{n-1}^V(r) = n-1$ then $r$ lies on edge $n-1$ and is the clockwise-most propagator supported on vertex $n$, so $I_n^V(r) = n$ and the remainder of $I_n^V$ proceeds identically to $I_{n-1}^V$. Thus $I_n^V(q) = n-5$, so by [cyclic intervals lemma or remark] we have $I_1^V(q) \in \{n-5,n-4\}$; in particular, $I_1^V(q)\neq n-3$.

We note for future reference that the arguments of the previous two paragraphs also imply that $n-2,n-1,n \not\in I_1^V$.

We can now describe $I_1^W$ in terms of $I_1^V$: when we start at vertex 1 in $W$ and apply the Grassmann necklace algorithm, $p$ is the \st{only remaining unassigned propagator when we reach vertex $n-3$}{\color{violet}last propagator to contribute}, and so we have $ I_1^{W}(p) = n-3$ and $I_1^W = I_1^V\cup \{n-3\}$.

@@

\begin{lem}\label{lem shape}
  Let $V$ and $W$ be as in Lemma~\ref{lem I}.
  The shape of the Le diagram of $V$ can be built from left to right of the following blocks: a rectangle which is 3 columns wide, one more column of the same height, and a partition shape with at most as many rows as the rectangle.
  The shape of the Le diagram of $W$ can be built from left to right of the following blocks: a rectangle with 3 columns and one more row than the first rectangle of $V$, and the same partition shape as in $V$.
\end{lem}

@@

Also by Lemma~\ref{lem I} we have $I_{n-1}^{W} = I_n^{V} \cup \{n-1\}$. Recall from the proof of Lemma \st{{\ref{lem I}}} {\color{violet} {\ref{lem shape}} }\sanote{change back if actually in 4.4} that $n-3,n-2,n-1,n \not\in I_1^V$; therefore $I_1^W\setminus I_{n-1}^W = (I_1^V \setminus I_n^V) \cup\{n-3\}$, and $n-3$ is maximal in this set. Similarly, 
\[I_{n-1}^W \setminus I_1^W = (I_n^V \setminus I_1^V) \cup \{n-1\} \subseteq \{n-1,n\},\]
where the final inclusion follows from the definition of Grassmann necklace.
\sanote{why only $\{n-1,n\}$? I'd believe an inclusion the other way}
\note{Definition of GN: $I_1 = (I_n\setminus\{n\})\cup\{\text{something}\}$}
In particular, $n-1$ is minimal in this set, so Algorithm~\ref{alg:GN to Le} yields a plus in the $(n-3) \rightarrow (n-1)$ position (i.e. the second box in the bottom row of the Le diagram of $W$) \hlfix{along with any plusses yielded by $I_n^V$.}{display seems to imply that there is exactly one such other $+$. Is this correct?}\note{If $n$ is non-supporting then $I_n^V \setminus I_1^V = \emptyset$ and we only get the $(n-3) \rightarrow (n-1)$ plus.}
\end{proof}

@@

  First note that a Wilson loop diagram $W$ with one propagator supported on vertices $i<i+1<j<j+1$ has a Le diagram consisting of a single row with $n-i$ boxes. The columns are labeled from left to right by $n, \ldots, i+1$. By Algorithm~\ref{alg:GN to Le} there are plusses in the $i+1$, $j$, and $j+1$ positions. \sanote{changed for grammar and notational consistency. check}

  Now consider Wilson loop diagrams with $k>1$ propagators.  By Lemma~\ref{lem uncovered} it suffices to prove the result for weakly admissible Wilson loop diagrams with $k$ propagators and no non-supporting vertices.  By Lemma~\ref{lem dihedral} it suffices to prove the result for at least one Wilson loop diagram from each dihedral orbit. In particular, we can restrict our attention to diagrams $W$ which have a propagator $p$ with the properties in Lemma~\ref{lem good p}.

We make one further simplification in order to eliminate the possibility that $n-2 \in I_{n-2}^V$ but $n-1 \not\in I_{n-2}^V$, which can only occur if our $W$ is in Case 2 of Figure~\ref{fig special p} and $n-1$ supports no propagators other than $p$. In this situation, flip $W$ on the line perpendicular to the $(n-2){th}$ edge to obtain a diagram with the configuration of Case 1.

\note{Sian rewrote above paragraph because their original version was wrong in multiple ways. Better?}
{\color{violet} I'm very confused about the previous paragraph. I thought that by constuction, in case 2, there can be exactly 2 propagators ending on edge $n-3$, $p$ and $q$. I also thought the distinguising feature between the two subcases of Figure 10 case 2 in Lemma 4.4 $I_{n-2}^W$ was the presence or absense of a propagator $r$ ending on edge $n-1$. If $r$ exists, $n-1 \in I_{n-2}^V$ and if  $r$ doesn't exist, $n-1 \not \in I_{n-2}^V$.}
